Amen to replication: What have we learned about networks in International relations 

### 2016-11-25 amenIntro/amenIntro.Rmd
final updates

---
title: "Networks Matter...or some nonsense like that"
output: 
      ioslides_presentation:
            smaller: true
---

@@

* Why are we meeting during Thanksgiving weekend...I didn't realize the date and none of you objected :)
* Anyhow...we are here to talk about conducting a meta-analysis of dyadic studies in political science using the Additive and Multiplicative Effects Model for Networks (AMEN)
* What I hope we find from this project is that using standard GLM approaches on dyadic data produces
      - biased estimates of the effect of independent variables
      - uncalibrated confidence intervals
      - and poor predictive performance.
* Anticipated outputs: 
      - One big meta-analysis piece in which we show the items in the list above to be true on average
      - A number of small replication pieces
      - New disciples to spread the gospel

@@

* Randomly divide the $n \times (n-1)$ data points into $S$ sets of roughly equal size, letting $s_{ij}$ be the set to which pair $\{ij\}$ is assigned.
* For each $s \in \{1, \ldots, S\}$:
	- Obtain estimates of the model parameters conditional on $\{y_{ij} : s_{ij} \neq s\}$, the data on pairs not in set $s$.
	- For pairs $\{kl\}$ in set $s$, let $\hat y_{kl} = E[y_{kl} | \{y_{ij} : s_{ij} \neq s\}]$, the predicted value of $y_{kl}$ obtained using data not in set $s$.

@@

* Teams of two, each of you will be paired with someone experienced in AME
	- Dorff + Foster
	- Gallop + Liu
	- Ward + Roberts
	- Me + Tellez 
* Claim the replications you want to do on Google sheets ... whoever gets there first wins.
	- Mansfield + Milner is already mine.
* <span style="color:red">**How many replications should we do?**</span>
* <span style="color:red">**Timeline?**</span>
* <span style="color:red">**What else?**</span>

>>>>

---
title: "Amen to replication: What have we learned about networks in International relations "
author: "Minhas, Dorff, Foster, Gallop, Liu, Roberts, Tellez, Ward"
output: 
      ioslides_presentation:
            smaller: true
---

@@

* Why are we meeting during Thanksgiving weekend...I didn't realize the date and none of you objected :)
* Anyhow...we are here to talk about conducting a meta-analysis of dyadic studies in political science using the Additive and Multiplicative Effects Model for Networks (AMEN)
* What I hope we find from this project is that using standard GLM approaches on dyadic data produces
      - biased estimates of the effect of independent variables
      - uncalibrated confidence intervals
      - and poor predictive performance.
* Anticipated outputs: 
      - One big meta-analysis piece in which we show the items in the list above to be true on average
      - <span style="color:red">**After**</span> big project is done, a number of small replication pieces
      - New disciples to spread the gospel

@@

* In each year, randomly divide the $n \times (n-1)$ data points into $S$ sets of roughly equal size, letting $s_{ij}$ be the set to which pair $\{ij\}$ is assigned.
* For each $s \in \{1, \ldots, S\}$:
	- Obtain estimates of the model parameters conditional on $\{y_{ij} : s_{ij} \neq s\}$, the data on pairs not in set $s$.
	- For pairs $\{kl\}$ in set $s$, let $\hat y_{kl} = E[y_{kl} | \{y_{ij} : s_{ij} \neq s\}]$, the predicted value of $y_{kl}$ obtained using data not in set $s$.

@@

* Teams of two, each of you will be paired with someone experienced in AME
	- Dorff + Foster
	- Gallop + Liu
	- Ward + Roberts
	- Me + Tellez 
* Claim the replications you want to do on Google sheets ... whoever gets there first wins.
	- Mansfield + Milner is already mine.
* <span style="color:red">**How many replications should we do?**</span>
	- I propose two.
* <span style="color:red">**Timeline?**</span>
	- AT LEAST ONE REPLICATION MODEL RUNNING BY JANUARY 1
	- Paper draft end of January
* <span style="color:red">**What else?**</span>
